---
title: "Sonde Locations for Cameron Peak Reservoir Study"
author: "Sam Struthers"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include= FALSE }
knitr::opts_chunk$set(echo = TRUE)
source("package_loader.R")

`%nin%` = Negate(`%in%`)

colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
      x)
  } else x
}

# Load data from sonde_locations.csv 
sonde_locations <- read.csv("data/potential_sonde_locations.csv", header = TRUE)%>%
  # seperate lat and long into seperate columns using , as a delimiter
    separate(lat_long, c("lat", "long"), sep = ",")%>%
    # convert lat and long to numeric
    mutate(lat = as.numeric(lat), long = as.numeric(long))%>%
    # using lat and long convert the dataframe into a sf object projected to crs 4326
    st_as_sf(coords = c("long", "lat"), crs = 4326)%>%
    #rename the column CPRW. to CPRW_Sensor?
    rename(CPRW_Sensor = CPRW.)

    #Create a map of the sonde locations using mapview
    # color blue if CPRW_Sensor = yes and don't color if CPRW_Sensor = no
    

clp_flowlines <- st_read("data/clp_flowlines")

```

## Map of site locations for sonde installations

-   [Proposed Sonde Locations:]{style="color:#43B54C"} Sites were Larimer County already has a radio tower set up and we could co-locate sondes to reducing install costs

-   [Current Water Quality Sondes:]{style="color:#808080"} Currently installed water quality sensors from City of Fort Collins or Warner College at the Mountain Campus

-   [CPRW Sonde?:]{style="color:#EE2939"} Locations were CPRW sondes could be used and benefit their ongoing long term monitoring

-   [Science Sonde:]{style="color:#2E5895"} Joe Wright Inflow Site were Larimer County does not have a radio tower set up and sonde would answer science questions rather than provide decision support to utility providers.

```{r, echo = FALSE}

  mapview::mapview(filter(sonde_locations, Final == "Yes"&CPRW_Sensor == "no"&sci == "no"), layer.name = "Proposed Sonde Locations",col.regions = "#43B54C", cex = 8)+
    mapview::mapview(filter(sonde_locations, current_network == "yes"), layer.name = "Current WQ Sensors",col.regions = "#808080", cex = 6)+
    mapview::mapview(filter(sonde_locations, CPRW_Sensor == "yes"),layer.name = "CPRW Sonde?", col.regions = "#EE2939", cex = 8)+
  mapview::mapview(filter(sonde_locations, sci == "yes"), layer.name = "Science Sonde",col.regions = "#2E5895", cex = 8)
```

# Map with Q/ Precip sites too

```{r, echo = FALSE}

dwr_sites <- c("JWCCHACO", "CLANSECO", "LAPLODCO","MICDCPCO", "LAPTUNCO", "GRNDRDCO")
larimer_sites <- c("11523","11517","6720", "11021", "6770", "11516", "11515", "11004", "11514", "11525", "11527","11530", "11531", "11528","11518")

usgs_sites <- c( "6746095", "6746110")

sensor_locations_all <- arrow::read_csv_arrow("data/compiled_q_locations.csv")%>%
  filter(!is.na(lat)&!is.na(long))%>%
  st_as_sf(coords = c("long", "lat"), crs = 4326)

DWR_present <- filter(sensor_locations_all, site_code %in% dwr_sites)

larimer_Q <- filter(sensor_locations_all, site_num %in% larimer_sites)

usgs <- filter(sensor_locations_all, site_num %in% usgs_sites)

discrete_sampling<- read_csv_arrow("data/cpf_sites.csv")%>%
  filter(!is.na(Lat)&!is.na(Long)& watershed %nin% "CLP Tributary" & site_code %nin% c("ARCH","LEGC", "ELC",  "TIMB"))%>%
  st_as_sf(coords = c("Long", "Lat"), crs = 4326)


 
mapview::mapview(larimer_Q, layer.name = "Larimer County Sensors",col.regions = "red", cex = 5)+
  mapview::mapview(usgs, layer.name = "USGS Sensors",col.regions = "blue", cex = 5)+
mapview::mapview(DWR_present, layer.name = "DWR Sensors",col.regions = "orange", cex = 5)+
    mapview::mapview(discrete_sampling, layer.name = "Grab Sample Locations", col.regions = "purple", cex = 5)+
   mapview::mapview(filter(sonde_locations, Final == "Yes"), layer.name = "Proposed Sonde Locations",col.regions = "#43B54C", cex = 8)
  
  
```



```{r, echo=FALSE}

concise_locations <- sonde_locations%>%
  select(site_name, Final, network = Installed)%>%
  mutate(network = ifelse(network == "No"))

mapview::mapview(filter(sonde_locations, Final == "Yes"&Installed == "Yes"), layer.name = "Current ROSS Network",col.regions = "#43B54C", cex = 8)+
      mapview::mapview(filter(sonde_locations, Final == "Yes" & Installed == "FCGOV"), layer.name = "Current Upper WQ Network",col.regions = "red", cex = 8)+
  mapview::mapview(filter(sonde_locations,site_name == "DWR - CLAFTCCO"), layer.name = " CLAFTCCO Co-location Site",col.regions = "purple", cex = 8)+
  mapview::mapview(filter(sonde_locations,Final == "Yes"& Installed == "No" &site_name != "DWR - CLAFTCCO"), layer.name = "Proposed Upper WQ Network",col.regions = "blue", cex = 8)
   

    mapview::mapshot(x = proposed_network, file = "test_obj.jpg",remove_controls = NULL )
    #c("layersControl", "zoomControl")
    
  mapview::mapview(filter(sonde_locations,Final == "Yes", Installed == "FCGOV"), layer.name = "Current Upper Network",col.regions = "red", cex = 6)


```

# Permit maps

```{r}

 map <- mapview(filter(sonde_locations, site_name == "USGS -  Joe Wright Res inflow"), layer.name = "Proposed JOEI",col.regions = "blue", cex = 8)+
  mapview(filter(sonde_locations, site_name == "USGS - JWCBJW"), layer.name = "Proposed JOEO",col.regions = "green4", cex = 8)+
  mapview(filter(sonde_locations, site_name == "Larimer - Chambers"), layer.name = "Proposed CHD",col.regions = "red", cex = 8)+
    mapview(filter(sonde_locations, site_name == "Larimer- Poudre Falls"), layer.name = "Proposed PFAL",col.regions = "grey", cex = 8)+
    mapview(filter(sonde_locations, site_name == "Fort Collins - Poudre Below Rustic"), layer.name = "Fort Collins: PBR",col.regions = "purple4", cex = 8)+
      mapview(filter(sonde_locations, site_name == "Larimer - SF Poudre at Pingree Park Road"), layer.name = "Proposed SFM",col.regions = "orange3", cex = 8)+
  mapview(filter(sonde_locations, site_name == "Fort Collins -  Manner's Bridge"), layer.name = "Fort Collins: Manner's Bridge",col.regions = "red", cex = 8, alpha.regions = 1)+
        mapview(filter(sonde_locations, site_name == "DWR - CLAFTCCO"), layer.name = "Proposed PBD",col.regions = "purple1", cex = 8)

#+
 # mapview(clp_flowlines,layer.name = "NHD Flowlines", col.regions = "#ADD8E6")
map


```

